PANCHANGE_analysis

### 2020-11-03 PANCHANGE_analysis.Rmd
Added subset of people who signed up 3 months prior to pandemic

>>>>

Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
```{r subsample for pre-pan sensitivity analysis}
# Participants who signed up in the three months before the pandemic began
dat.prepan_sensitivity_3months <- dat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
      data_group_gad == "Prepandemic and baseline data" |
      data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "Baseline and retrospective data" |
      data_group_phq == "Prepandemic and baseline data" |
      data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "Baseline and retrospective data" |
      data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "Baseline and retrospective data" |
      data_group_ocir == "Prepandemic and baseline data" |
      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_march_1_numeric == 1  & # Exclude participants that signed up after the 1. March 
      (startDate.prepandemic < date_3months_prior_march_1st), # The GLAD sign up is dated after the cut off
  )
```
